---
title: "Walker experiment"
author: "Lisa Koßmann, Alexander (Sasha) Pastukhov"
date: "31 1 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(bayestestR)
library(betareg)
library(boot)
library(brms)
library(extrafont)
library(fs)
library(ggbeeswarm)
library(ggpmisc)
library(ggpubr)
library(glue)
library(grid)
library(patchwork)
library(reshape2)
library(tidyverse)

extrafont::loadfonts(quiet = TRUE)

# source does not play well with unicode on Windows
eval(parse('common_utilities.R', encoding = 'UTF-8'))
```



# Importing data
```{r Import}
read_walker_csv <- function(filename){
  read_csv(filename, 
           col_types=cols(
                .default = col_double(),
                Participant = col_character(),
                Session = col_character(),
                Block = col_double(),
                OnsetDelay = col_double(),
                Condition = col_character(),
                Percept = col_character(),
                Time = col_double()
              )) %>%
    mutate(SessionTag = case_when(stringr::str_detect(filename, "addendumer") ~ "Addendumer",
                                  "Shift" %in% names(.) ~ "Addendum", 
                                  TRUE ~ "Main"))
}

reports <- 
  # 1. Load files
  purrr::map_dfr(dir_ls(path = "Data", glob  = "*walker*.csv"),
                 ~read_walker_csv(.)) %>%
  
  # 2. Compute duration PER BLOCK. Inside mutate use "lead(Time)".
  group_by(Participant, Session, Block) %>%
  mutate(Duration = lead(Time) - Time) %>%
  ungroup() %>%

  # 3. Drop "end" Percept
  filter(Percept != "end")%>%
  
  # 4. Renaming Percepts
  mutate(RawPercept = Percept, 
         Percept=as.factor(Percept),
         Percept=fct_recode(Percept, "congruent"="up", "incongruent"="down"))%>%
  mutate(NotInteracting=as.numeric(Distance > 0 | Shift != 0))
```


## Distance vertical condition

```{r}
vertical_distance <- 
  reports %>%
  filter(SessionTag == "Main", Condition %in% c("Control", "Distance"))%>%
  dplyr::mutate(DistanceAsFactor = as.factor(Distance),
                DistanceAsFactor = fct_relevel(DistanceAsFactor,"0", "1", "2", "3", "4")) %>%
  
  # computing Pcongurent for each participant and distance seperatly
  dplyr::group_by(Participant, Distance, DistanceAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
                   CongruentDur = sum(Duration[Percept=="congruent"]),
                   Pcongruent = CongruentDur / TotalDuration,
                   .groups="drop") %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005)%>%

  # duplicating distance as Term for common BRMS model use
  dplyr::mutate(Term = Distance,
                TermAsFactor = DistanceAsFactor)%>%
  mutate(NotInteracting=as.numeric(Distance > 0 ))
```

### Precompiling BRMS models

```{r brms models}
independent_prototype <- brm(PcongruentAdj ~ (1|Participant),
                           family=Beta(),
                           chains=0, # this means that model is never sampled
                           data=vertical_distance)

perceptual_coupling_prototype <- brm(PcongruentAdj ~ Term + (1|Participant),
                     family=Beta(),
                     data=vertical_distance,
                     chains=0, # this means that model is never sampled
                     prior=c(prior(normal(0, 1), class="b")))

physics_prototype <- brm(PcongruentAdj ~ NotInteracting + (1|Participant),
                          family=Beta(),
                          data=vertical_distance,
                          chains=0,
                          prior=c(prior(normal(0, 1), class="b")))

interaction_prototype <- brm(PcongruentAdj ~ Term + Term:NotInteracting + (1|Participant),
                      family=Beta(),
                      data=vertical_distance,
                      chains=0,
                      prior=c(prior(normal(0, 1), class="b")))


pairwise_comparison_prototype <- brm(PcongruentAdj ~ TermAsFactor + (1|Participant),
                        family=Beta(),
                        data=vertical_distance,
                        chains=0, # this means that model is never sampled
                        prior=c(prior(normal(0,1), class="b")))

prototypes <- list("Independent" = independent_prototype,
                   "Perceptual Coupling" = perceptual_coupling_prototype, 
                   "Physics" = physics_prototype,
                   "Interaction" = interaction_prototype)
```



### Fitting vertical distance condition via brms

```{r Fitting vertical distance as a continuous variable via brms}
set.seed(5515605)
vertical_fits <- purrr::map(prototypes, ~fit_prototype(., vertical_distance))
vertical_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, vertical_distance, add_loo = FALSE)
```

### Compare models

```{r}
compare_models(vertical_fits)
```

### vertical distance model predictions

```{r vertical distance as continuous predictions}
# predict GROUP-LEVEL Pcorotation
vertical_distance_fit_predictions <- 
  predict(vertical_fits$`Perceptual Coupling`,
          newdata = data.frame(Term = seq(0, 4.1, 0.1)),
          probs = c(0.055, 0.25, 0.75, 0.945),
          re_formula = NA) %>%
  as_tibble() %>%
  add_column(Term = seq(0, 4.1, 0.1)) %>%
  rename(Distance = Term)
```

### vertical distance summary plot
```{r distance summary plot}
vertical_distance_plot <-
  ggplot(data=vertical_distance_fit_predictions, aes(x=Distance, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=vertical_distance, method="tukeyDense", width=0.2,
                  aes(x=Distance, group=Distance, y=Pcongruent)) +
  scale_x_continuous(name = "Vertical Distance (degrees)", breaks = unique(vertical_distance$Distance),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_predicted_difference(vertical_pairwise_comparison))) +
  scale_y_continuous(name="Pcongruent") +
  plot_theme()
vertical_distance_plot
```

## Distance horizontal condition

```{r}
horizontal_distance <- 
  reports %>%
  filter(SessionTag == "Addendum", Condition %in% c("Control", "Shift"))%>%
  dplyr::mutate(ShiftAbs = abs(Shift),
                ShiftAsFactor = as.factor(ShiftAbs),
                ShiftAsFactor= fct_relevel(ShiftAsFactor,"0", "1", "2", "3", "4")) %>%
  
  # computing Pcongurent for each participant and distance seperatly
  dplyr::group_by(Participant, ShiftAbs, ShiftAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
            # if value in the brackets is true it'll be considered if not it will not
            CongruentDur = sum(Duration[Percept=="congruent"]),
            Pcongruent = CongruentDur / TotalDuration, .groups="drop") %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005)%>%

  # duplicating distance as Term for common BRMS model use
  dplyr::mutate(Term = ShiftAbs,
                TermAsFactor = ShiftAsFactor)%>%
  mutate(NotInteracting=as.numeric(ShiftAbs != 0))
```

### Fitting horizontal distance condition via brms

```{r Fitting Horizontal distance as a continuous variable via brms}
set.seed(3829937)
horizontal_fits <- purrr::map(prototypes, ~fit_prototype(., horizontal_distance))
horizontal_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, horizontal_distance, add_loo = FALSE)
```

### Compare models

```{r}
compare_models(horizontal_fits)
```

### horizontal_distance model predictions

```{r horizontal_distance as continuous predictions}
# predict GROUP-LEVEL Pcorotation
horizontal_distance_fit_predictions <- 
  predict(horizontal_fits$`Perceptual Coupling`,
          newdata = data.frame(Term = seq(0, 4.1, 0.1)),
          probs = c(0.055, 0.25, 0.75, 0.945),
          re_formula = NA) %>%
  data.frame() %>%
  add_column(Term = seq(0, 4.1, 0.1)) %>%
  rename(ShiftAbs = Term)
```

### horizontal distance summary plot
```{r horizontal_distance plot}
horizontal_distance_plot <-
  ggplot(data=horizontal_distance_fit_predictions, aes(x=ShiftAbs, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=horizontal_distance, method="tukeyDense", width=0.2,
                  aes(x=ShiftAbs, group=ShiftAbs, y=Pcongruent)) +
  scale_x_continuous(name = "Horizontal Distance (degrees)", breaks = unique(horizontal_distance$ShiftAbs),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_predicted_difference(horizontal_pairwise_comparison))) +
  scale_y_continuous(name="Pcongruent") +
  plot_theme()
horizontal_distance_plot
```
## Sphere ambiguity condition
```{r}
sphere_ambiguity <-
  reports %>%
  filter(SessionTag == "Main", Condition %in% c("Control", "Sphere ambiguity"))%>%
  dplyr::mutate(SphereDisambiguationAbs = abs(SphereDisambiguation), 
                SphereDisambiguationAsFactor = as.factor(SphereDisambiguationAbs),
                SphereDisambiguationAsFactor = fct_relevel(SphereDisambiguationAsFactor, "0", "0.25", "1")) %>%
  
  ## computing Pcongurent for each participant and disambiguation seperatly
  dplyr::group_by(Participant, SphereDisambiguationAbs, SphereDisambiguationAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
            # if value in the brackets is true it'll be considered if not it will not
            CongruentDur = sum(Duration[Percept=="congruent"]),
            Pcongruent = CongruentDur / TotalDuration,
            .groups="drop") %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005) %>%             

  # duplicating Sphere ambiguity as Term for common BRMS model use
  dplyr::mutate(Term = SphereDisambiguationAbs,
                TermAsFactor = SphereDisambiguationAsFactor)%>%
  dplyr::mutate(NotInteracting=1)
```

### Fitting sphere ambiguity condition via brms

```{r Fitting sphere ambiguity as a continuous variable via brms}
set.seed(5515605)
sphere_fits <- purrr::map(prototypes, ~fit_prototype(., sphere_ambiguity))
sphere_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, sphere_ambiguity, add_loo = FALSE)
```


### Compare models

```{r}
compare_models(sphere_fits)
```

### sphere ambiguity model predictions

```{r sphere ambiguity as continuous predictions}
# predict GROUP-LEVEL Pcorotation
sphere_ambiguity_fit_predictions <- 
  predict(sphere_fits$`Perceptual Coupling`,
          newdata = data.frame(Term = seq(0, 1.1, 0.1)),
          probs = c(0.055, 0.25, 0.75, 0.945),
          re_formula = NA) %>%
  as_tibble() %>%
  add_column(Term = seq(0, 1.1, 0.1)) %>%
  rename(SphereDisambiguationAbs = Term)
```

### sphere ambiguity summary plot
```{r sphere ambiguity plot}
sphere_ambiguity_plot <-
  ggplot(data=sphere_ambiguity_fit_predictions, aes(x=SphereDisambiguationAbs, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=sphere_ambiguity, method="tukeyDense", width=0.04,
                  aes(x=SphereDisambiguationAbs, group=SphereDisambiguationAbs, y=Pcongruent)) +
  scale_x_continuous(name = "Sphere Disambiguation (degrees)", breaks = unique(sphere_ambiguity$SphereDisambiguationAbs),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_predicted_difference(sphere_pairwise_comparison))) +
  scale_y_continuous(name="Pcongruent", limits= c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  plot_theme()
sphere_ambiguity_plot
```
### Walker ambiguity condition

```{r}
walker_ambiguity <-
  reports %>%
  filter(SessionTag == "Main", Condition %in% c("Control", "Walker ambiguity"))%>%
  dplyr::mutate(WalkerDisambiguationAbs = abs(WalkerDisambiguation), 
                WalkerDisambiguationAsFactor = as.factor(WalkerDisambiguationAbs),
                WalkerDisambiguationAsFactor = fct_relevel(WalkerDisambiguationAsFactor, "0", "0.25", "1")) %>%
  
  ## computing Pcongurent for each participant and disambiguation seperatly
  dplyr::group_by(Participant, WalkerDisambiguationAbs, WalkerDisambiguationAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
            # if value in the brackets is true it'll be considered if not it will not
            CongruentDur = sum(Duration[Percept=="congruent"]),
            Pcongruent = CongruentDur / TotalDuration,
            .groups="drop") %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005) %>%             

  # duplicating Sphere ambiguity as Term for common BRMS model use
  dplyr::mutate(Term = WalkerDisambiguationAbs,
                TermAsFactor = WalkerDisambiguationAsFactor)%>%
  dplyr::mutate(NotInteracting=1)
```

### Fitting walker ambiguity condition via brms
```{r Fitting walker ambiguity as a continuous variable via brms}
set.seed(5515605)
walker_fits <- purrr::map(prototypes, ~fit_prototype(., walker_ambiguity))
walker_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, walker_ambiguity, add_loo = FALSE)
```

### Compare models
```{r}
compare_models(walker_fits)
```

### walker ambiguity model predictions

```{r walker ambiguity as continuous predictions}
# predict GROUP-LEVEL Pcorotation
walker_ambiguity_fit_predictions <- 
  predict(walker_fits$`Perceptual Coupling`,
          newdata = data.frame(Term = seq(0, 1.1, 0.1)),
          probs = c(0.055, 0.25, 0.75, 0.945),
          re_formula = NA) %>%
  as_tibble() %>%
  add_column(Term = seq(0, 1.1, 0.1)) %>%
  rename(WalkerDisambiguationAbs = Term)
```

### walker ambiguity summary plot
```{r walker ambiguity plot}
walker_ambiguity_plot <-
  ggplot(data=walker_ambiguity_fit_predictions, aes(x=WalkerDisambiguationAbs, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=walker_ambiguity, method="tukeyDense", width=0.07,
                  aes(x=WalkerDisambiguationAbs, group=WalkerDisambiguationAbs, y=Pcongruent)) +
  scale_x_continuous(name = "Walker Disambiguation (degrees)",limits= c(-0.09, 1.09),  breaks = unique(walker_ambiguity$WalkerDisambiguationAbs),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_predicted_difference(walker_pairwise_comparison))) +
  scale_y_continuous(name="Pcongruent", limits= c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  plot_theme()
walker_ambiguity_plot
```

## All plots together

```{r}
vertical_distance_plot/horizontal_distance_plot  + 
  plot_annotation(tag_levels= "A")

# ggsave('figure-05-walker.pdf', width=14, height=20, units="cm", device=cairo_pdf)
ggsave('figure-03-walker-distance.png', width=14, height=14, units="cm")
ggsave('figure-03-walker-distance.svg', width=14, height=14, units="cm")


sphere_ambiguity_plot / walker_ambiguity_plot + 
  plot_annotation(tag_levels= "A")

# ggsave('figure-05-walker.pdf', width=14, height=20, units="cm", device=cairo_pdf)
ggsave('figure-04-walker-ambiguity.png', width=14, height=14, units="cm")
ggsave('figure-04-walker-ambiguity.svg', width=14, height=14, units="cm")
```

## Single Object report walker

```{r}
SOR_walker <- 
  reports %>%
  filter(SessionTag == "Addendumer", Condition %in% c("Walker"))%>%
    dplyr::mutate(IsCongruent = (SphereBias == -1 & RawPercept == "up") | (SphereBias == 1 & RawPercept == "down")) %>%
    dplyr::mutate(ShiftAbs = abs(Shift),
                ShiftAsFactor = as.factor(ShiftAbs),
                ShiftAsFactor = fct_relevel(ShiftAsFactor, "0","2","4")) %>%

    ## computing Pcongurent for each participant and disambiguation seperatly
    dplyr::group_by(Participant, ShiftAbs, ShiftAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
            # if value in the brackets is true it'll be considered if not it will not
            CongruentDur = sum(Duration[IsCongruent=="TRUE"]),
            Pcongruent = CongruentDur / TotalDuration) %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005)%>%
             
# duplicating Sphere ambiguity as Term for common BRMS model use
  dplyr::mutate(Term = ShiftAbs,
                TermAsFactor = ShiftAsFactor)%>%
  dplyr::mutate(NotInteracting=as.numeric(ShiftAbs != 0))
```

### Fitting single object report walker condition via brms

```{r Fitting SOR walker as a continuous variable via brms}
set.seed(5515605 )
# error here: 'beta' requires response greater than zero
SOR_walker_perceptual_coupling_model <- fit_prototype(perceptual_coupling_prototype, SOR_walker)
SOR_walker_independent_model <- fit_prototype(independent_prototype, SOR_walker)
SOR_walker_physics <- fit_prototype(physics_prototype, SOR_walker)
SOR_walker_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, SOR_walker, add_loo = FALSE)
```

### Compare models

```{r}
compare_models(SOR_walker_perceptual_coupling_model, SOR_walker_independent_model, SOR_walker_physics)
```

### walker SOR model predictions

```{r walker SOR as continuous predictions}
# predict GROUP-LEVEL Pcorotation
SOR_walker_fit_predictions <- predict(SOR_walker_perceptual_coupling_model,
                                    newdata = data.frame(Term = seq(0, 4.2)),
                                    probs = c(0.055, 0.25, 0.75, 0.945),
                                    re_formula = NA) %>%
  data.frame() %>%
  add_column(Term = seq(0, 4.2)) %>%
  rename(ShiftAbs = Term)
```

### walker SOR summary plot
```{r walker SOR plot}
SOR_walker_plot <-
  ggplot(data=SOR_walker_fit_predictions, aes(x=ShiftAbs, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=SOR_walker, method="tukeyDense", width=0.2,
                  aes(x=ShiftAbs, group=ShiftAbs, y=Pcongruent)) +
  scale_x_continuous(name = "Shift (degrees)", breaks = unique(SOR_walker$ShiftAbs),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_betas(SOR_walker_pairwise_comparison))) +
  scale_y_continuous(name="Pcongruent", limits= c(0, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  plot_theme()
SOR_walker_plot
```

## Single Object report sphere

```{r single condition sphere}
SOR_sphere <- 
  reports %>%
  filter(SessionTag=="Addendumer", Condition %in% c("Sphere")) %>%
  mutate(InBiasDirection = (SphereBias == -1 & Percept == "right") | (SphereBias == 1 & Percept == "left")) %>%
  
  # absolute shift
  dplyr::mutate(ShiftAbs = abs(Shift),
                ShiftAsFactor = as.factor(ShiftAbs),
                ShiftAsFactor = fct_relevel(ShiftAsFactor, "0","2","4")) %>%
  
  # computing Pcongurent for each participant and Shift seperatly
  dplyr::group_by(Participant, ShiftAbs, ShiftAsFactor) %>%
  dplyr::summarize(TotalDuration = sum(Duration),
                   # if value in the brackets is true it'll be considered if not it will not
                   ConsistentDur= sum(Duration[InBiasDirection=="TRUE"]),               
                   Pcongruent = ConsistentDur / TotalDuration) %>%
  dplyr::mutate(PcongruentAdj = Pcongruent*0.999+0.0005)%>%
# duplicating Sphere ambiguity as Term for common BRMS model use
  dplyr::mutate(Term = ShiftAbs,
                TermAsFactor = ShiftAsFactor)%>%
  dplyr::mutate(NotInteracting=as.numeric(ShiftAbs != 0))
```

### Fitting single object report sphere condition via brms

```{r Fitting SOR sphere as a continuous variable via brms}
set.seed(5515605 )
# error here: 'beta' requires response greater than zero
SOR_sphere_perceptual_coupling_model <- fit_prototype(perceptual_coupling_prototype, SOR_sphere)
SOR_sphere_independent_model <- fit_prototype(independent_prototype, SOR_sphere)
SOR_sphere_physics <- fit_prototype(physics_prototype, SOR_sphere)
SOR_sphere_pairwise_comparison <- fit_prototype(pairwise_comparison_prototype, SOR_sphere, add_loo = FALSE)
```


### Compare models

```{r}
compare_models(SOR_sphere_perceptual_coupling_model, SOR_sphere_independent_model, SOR_sphere_physics)
```
### Sphere SOR model predictions

```{r sphere SOR as continuous predictions}
# predict GROUP-LEVEL Pcorotation
SOR_sphere_fit_predictions <- predict(SOR_sphere_perceptual_coupling_model,
                                    newdata = data.frame(Term = seq(0, 4.2)),
                                    probs = c(0.055, 0.25, 0.75, 0.945),
                                    re_formula = NA) %>%
  data.frame() %>%
  add_column(Term = seq(0, 4.2)) %>%
  rename(ShiftAbs = Term)
```

### Sphere SOR summary plot
```{r walker SOR plot}
SOR_sphere_plot <-
  ggplot(data=SOR_sphere_fit_predictions, aes(x=ShiftAbs, y=Estimate)) + 
  geom_ribbon(aes(ymin=Q5.5, ymax=Q94.5), alpha= 0.25) + 
  geom_ribbon(aes(ymin=Q25, ymax=Q75), alpha= 0.25) + 
  geom_line() +
  geom_hline(yintercept = 0.5, color="white", size= 1) +
  geom_quasirandom(data=SOR_sphere, method="tukeyDense", width=0.2,
                  aes(x=ShiftAbs, group=ShiftAbs, y=Pcongruent)) +
  scale_x_continuous(name = "Shift (degrees)", breaks = unique(SOR_sphere$ShiftAbs),
                     sec.axis =  dup_axis(name=NULL, labels=compute_factor_level_betas(SOR_sphere_pairwise_comparison))) +
  scale_y_continuous(name="Pconsistent", limits= c(0.5, 1), breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  plot_theme()

SOR_sphere_plot
```

```{r}
SOR_sphere_plot/SOR_walker_plot  + 
  plot_annotation(tag_levels= "A")

# ggsave('figure-05-walker.pdf', width=14, height=20, units="cm", device=cairo_pdf)
ggsave('figure-05-walker-single.png', width=14, height=14, units="cm")
ggsave('figure-05-walker-single.svg', width=14, height=14, units="cm")
```